---
title: "Sentinel-5P OFFL NO2 — historical-record homogeneity audit (BAAQMD)"
subtitle: >
  Bay Area Air Quality Episode Finder — supporting analysis.
  Audit and retrospective baseline-robustness study. The notebook's
  computations select nothing; the project owner's recorded decision
  (2026-07-19) is in Section 8.
output:
  html_document:
    toc: true
    toc_depth: 3
    number_sections: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo = TRUE,
  message = FALSE,
  warning = TRUE,
  fig.width = 9,
  fig.height = 4.5
)
```

# Purpose and scope

This notebook analyses the yearly audit tables exported by
`earthengine/exploration/07_s5p_no2_historical_homogeneity_export.js`
to support the **historical-record homogeneity decision** for the
Sentinel-5P OFFL tropospheric NO2 record over the BAAQMD jurisdiction
(gate step 8 in `docs/roadmap.md`; audit background in
`docs/methodology.md`).

Every value analysed here is a Sentinel-5P **tropospheric vertical NO2
column** quantity (mol/m²) — an indicator of column patterns. It is not
a ground-level concentration, not an AQI value, not a health measure,
and not an episode result.

The notebook also contains a **retrospective baseline-robustness
study** (Section 7): under the project owner's policy-level adoption of
Outcome B (the Earth Engine OFFL record is usable for exploratory
historical analysis but must not be treated as unconditionally
homogeneous), it evaluates practical historical-pool variants of the
accepted exploratory script 06 baseline across all eligible target
months from 2020 onward. That study informed the owner's final
decision and baseline policy, recorded in Section 8 (2026-07-19).

**What this notebook does NOT do:**

- It does **not** choose the homogeneity outcome or the baseline
  policy. Both are **project owner decisions**, recorded 2026-07-19
  after review of the accepted full-history report: Outcome B with an
  explicit baseline policy (Section 8 and `docs/methodology.md`).
- It does **not** select a baseline restriction, historical-pool
  variant, or coverage threshold by computation. Section 7 reports
  robustness evidence only; its coverage values were sensitivity
  candidates (the owner's recorded policy adopts **no hard
  valid-area-fraction exclusion**).
- It does **not** calculate processor correction factors.
- It does **not** treat temporal discontinuities as proof of
  retrieval-processing effects — season, meteorology, emission trends
  (including the 2020 pandemic period), and coverage changes are
  plausible confounders throughout.
- It does **not** define final thresholds, baselines, persistence
  rules, spatial-extent rules, or episode labels.

**Data source:** local CSV files exported by script 07 (Google Drive
downloads placed in the configured directories below). This notebook
does **not** download data automatically.

# Packages

Deliberately modest, ordinary packages for reproducible analysis:

```{r packages}
# readr    - CSV import with explicit column types
# dplyr    - data manipulation
# tidyr    - reshaping (pivots, completing date grids)
# purrr    - functional iteration over files / variants
# stringr  - set-string parsing (';'-joined export cells)
# ggplot2  - figures
# lubridate- calendar arithmetic (months, years, seasons)
# scales   - axis formatting
# knitr    - tables (kable)
library(readr)
library(dplyr)
library(tidyr)
library(purrr)
library(stringr)
library(ggplot2)
library(lubridate)
library(scales)
library(knitr)
```

# Configuration

```{r config}
# All data paths are anchored to the repository root so knitting does
# not depend on the working directory (RStudio knit button,
# rmarkdown::render() from the repo root, or knitr::knit() elsewhere).
# During a knit the search starts from this file's own directory; in
# interactive use it starts from the working directory.
find_repo_root <- function(start) {
  markers <- c("bay_area_air_quality_episode_finder_overview.md", ".git")
  current <- normalizePath(start, winslash = "/", mustWork = TRUE)
  repeat {
    if (any(file.exists(file.path(current, markers)))) return(current)
    parent <- dirname(current)
    if (identical(parent, current)) {
      stop("Repository root not found above '", start, "' (looked for: ",
           paste(markers, collapse = ", "),
           "). Knit or run this notebook from inside the repository.")
    }
    current <- parent
  }
}
knit_input <- tryCatch(knitr::current_input(dir = TRUE),
                       error = function(e) NULL)
repo_root <- find_repo_root(
  if (!is.null(knit_input)) dirname(knit_input) else getwd())

config <- list(
  # Local directories holding the script 07 exports (no auto-download),
  # anchored to the repository root.
  daily_dir     = file.path(repo_root, "data", "homogeneity"),
  products_dir  = file.path(repo_root, "data", "homogeneity"),
  manifest_path = file.path(repo_root, "data", "homogeneity",
                            "s5p_no2_homogeneity_manifest.csv"),

  # Export-file conventions (must match script 07 CONFIG).
  daily_pattern    = "^s5p_no2_homogeneity_daily_\\d{4}\\.csv$",
  products_pattern = "^s5p_no2_homogeneity_products_\\d{4}\\.csv$",
  set_separator    = ";",
  missing_token    = "(missing)",

  # Diagnostic display conventions ONLY - none of these is a decided
  # scientific threshold or method:
  transition_window_days = 60,  # +/- days shown around a metadata change
  historical_years_diagnostic = 3,  # mirrors the script 06 exploratory
                                    # baseline default (1-5, default 3)
  small_sample_flag_n = 10,     # display flag for small baseline samples

  # Retrospective baseline-robustness study (Section 7).
  # First target year of the retrospective evaluation (owner-directed).
  retrospective_start_year = 2020,
  # Coverage-sensitivity CANDIDATES for the prior-three-years baseline
  # (0 = any valid coverage). Sensitivity candidates only - none is an
  # adopted threshold.
  coverage_candidates = c(0, 0.20, 0.40, 0.60)
)

# Expected schemas (fixed column order set by script 07 `selectors`).
expected_daily_cols <- c(
  "local_date", "regional_mean_no2", "valid_area_fraction",
  "has_valid_value", "daily_source_asset_count",
  "daily_distinct_product_count", "daily_distinct_orbit_count",
  "valid_contributor_count", "has_contributing_non_nominal",
  "contributing_product_quality_values",
  "contributing_processor_version_set",
  "contributing_algorithm_version_set",
  "contributing_processing_status_set",
  "contributing_spatial_resolution_set",
  "contributing_product_ids", "contributing_orbits"
)
expected_product_cols <- c(
  "local_date", "system_time_start", "PRODUCT_ID", "ORBIT",
  "PROCESSOR_VERSION", "ALGORITHM_VERSION", "PRODUCT_QUALITY",
  "PROCESSING_STATUS", "SPATIAL_RESOLUTION"
)
expected_manifest_cols <- c(
  "export_year", "requested_start", "requested_end",
  "latest_represented_local_date", "last_included_local_date",
  "actual_collection_start", "actual_collection_end", "dataset_id",
  "band", "boundary_asset", "boundary_filter", "timezone", "crs",
  "scale_m", "daily_combination_rule", "export_created_at",
  "script_identifier"
)
```

```{r availability}
daily_files <- sort(list.files(config$daily_dir,
                               pattern = config$daily_pattern,
                               full.names = TRUE))
product_files <- sort(list.files(config$products_dir,
                                 pattern = config$products_pattern,
                                 full.names = TRUE))
data_available <- length(daily_files) > 0 &&
  length(product_files) > 0 &&
  file.exists(config$manifest_path)

if (!data_available) {
  cat("Exported audit files were NOT found in the configured",
      "directories.\n",
      "Run script 07 in the Earth Engine Code Editor, start the export",
      "tasks,\n",
      "download the CSVs from Drive into the configured directories,",
      "then re-knit.\n",
      "Analysis chunks below are skipped (eval = FALSE) until then.\n")
}
```

# Section 1 — Import and schema validation

Import notes: an **empty** `regional_mean_no2` cell means the day had no
valid area (read as `NA`; script 07 exports the row anyway — days are
never silently omitted). In set-string cells, an **empty string** means
"no values", which is distinct from the literal `` `r "(missing)"` ``
token (a product present but lacking that metadata property). The daily
`contributing_*` metadata columns are **contributor-scoped**: derived
only from products with actual valid BAAQMD pixels, so a day with no
valid contributors has empty contributor-scoped set strings **by
design**. The product metadata table is the **collection-wide** record
of every footprint-intersecting asset; the two are analysed separately
throughout this notebook and never merged.

```{r import, eval = data_available}
check_schema <- function(df, expected, label) {
  missing_cols <- setdiff(expected, names(df))
  extra_cols   <- setdiff(names(df), expected)
  if (length(missing_cols) > 0 || length(extra_cols) > 0) {
    stop("Schema mismatch in ", label,
         " - missing: [", paste(missing_cols, collapse = ", "),
         "]; unexpected: [", paste(extra_cols, collapse = ", "), "]")
  }
  invisible(TRUE)
}

daily_col_types <- cols(
  local_date = col_date(format = "%Y-%m-%d"),
  regional_mean_no2 = col_double(),
  valid_area_fraction = col_double(),
  has_valid_value = col_integer(),
  daily_source_asset_count = col_integer(),
  daily_distinct_product_count = col_integer(),
  daily_distinct_orbit_count = col_integer(),
  valid_contributor_count = col_integer(),
  has_contributing_non_nominal = col_integer(),
  .default = col_character()
)
product_col_types <- cols(
  local_date = col_date(format = "%Y-%m-%d"),
  system_time_start = col_double(),
  .default = col_character()
)
manifest_col_types <- cols(
  export_year = col_integer(),
  scale_m = col_double(),
  .default = col_character()
)

daily <- map_dfr(daily_files, function(f) {
  df <- read_csv(f, col_types = daily_col_types, na = c(""))
  check_schema(df, expected_daily_cols, basename(f))
  df$source_file <- basename(f)
  df
})
# Empty set-strings arrive as NA under na = c(""); restore them as
# empty strings so "no values" stays distinct from a missing column.
set_cols <- c("contributing_product_quality_values",
              "contributing_processor_version_set",
              "contributing_algorithm_version_set",
              "contributing_processing_status_set",
              "contributing_spatial_resolution_set",
              "contributing_product_ids", "contributing_orbits")
daily <- daily %>%
  mutate(across(all_of(set_cols), ~ replace_na(.x, "")))

products <- map_dfr(product_files, function(f) {
  df <- read_csv(f, col_types = product_col_types, na = c(""))
  check_schema(df, expected_product_cols, basename(f))
  df$source_file <- basename(f)
  df
})

manifest <- read_csv(config$manifest_path,
                     col_types = manifest_col_types, na = c(""))
check_schema(manifest %>% select(-any_of("source_file")),
             expected_manifest_cols, basename(config$manifest_path))

kable(manifest, caption = "Audit manifest (one row per exported year).")
```

```{r import-consistency, eval = data_available}
# Internal consistency: has_valid_value == 1 must coincide with a
# non-missing regional mean. Mismatches are REPORTED, never dropped.
consistency <- daily %>%
  mutate(mean_is_na = is.na(regional_mean_no2)) %>%
  count(has_valid_value, mean_is_na)
kable(consistency,
      caption = paste("has_valid_value vs missing regional mean",
                      "(expected: 1 pairs with FALSE, 0 with TRUE)."))

inconsistent_rows <- daily %>%
  filter((has_valid_value == 1) == is.na(regional_mean_no2))
if (nrow(inconsistent_rows) > 0) {
  kable(inconsistent_rows %>%
          select(local_date, regional_mean_no2, has_valid_value,
                 valid_area_fraction, source_file),
        caption = "INCONSISTENT rows (investigate before relying on them).")
} else {
  cat("No has_valid_value / regional-mean inconsistencies found.\n")
}

cat("Daily rows:", nrow(daily),
    "| product-asset rows:", nrow(products),
    "| years in manifest:", paste(manifest$export_year, collapse = ", "),
    "\n")
```

# Section 2 — Duplicate-date and missing-year checks

```{r duplicates, eval = data_available}
# Duplicate local dates across the combined daily table (expected: none;
# yearly windows are non-overlapping).
dup_dates <- daily %>% count(local_date) %>% filter(n > 1)
if (nrow(dup_dates) > 0) {
  kable(dup_dates, caption = "DUPLICATE local dates (investigate).")
} else {
  cat("No duplicate local dates.\n")
}

# Duplicate PRODUCT_ID rows in the product table. Two rows in the SAME
# file can be legitimate (the official antimeridian two-asset
# exception); the same PRODUCT_ID in DIFFERENT yearly files suggests a
# product whose assets straddled a local-year boundary and was split
# between exports (script 07 documents this; nothing is deduplicated
# silently here).
dup_products <- products %>%
  group_by(PRODUCT_ID) %>%
  summarise(n_rows = n(),
            n_files = n_distinct(source_file), .groups = "drop") %>%
  filter(n_rows > 1)
if (nrow(dup_products) > 0) {
  kable(dup_products,
        caption = paste("PRODUCT_ID values with multiple asset rows",
                        "(same file: antimeridian exception;",
                        "multiple files: year-boundary straddle)."))
} else {
  cat("Every PRODUCT_ID has exactly one asset row.\n")
}

# Missing years and missing dates against the manifest's requested
# windows (requested_end is END-EXCLUSIVE).
requested_days <- manifest %>%
  mutate(start = as.Date(requested_start),
         end_exclusive = as.Date(requested_end)) %>%
  rowwise() %>%
  reframe(local_date = seq.Date(start, end_exclusive - 1, by = "day"))
missing_days <- requested_days %>% anti_join(daily, by = "local_date")
extra_days <- daily %>% anti_join(requested_days, by = "local_date")
cat("Requested days:", nrow(requested_days),
    "| exported daily rows:", nrow(daily),
    "| requested-but-absent:", nrow(missing_days),
    "| exported-but-unrequested:", nrow(extra_days), "\n")
if (nrow(missing_days) > 0) {
  kable(head(missing_days, 30),
        caption = "Requested dates ABSENT from the daily export (first 30).")
}

years_in_files <- sort(unique(year(daily$local_date)))
missing_years <- setdiff(manifest$export_year, years_in_files)
if (length(missing_years) > 0) {
  cat("Manifest years with no daily rows:",
      paste(missing_years, collapse = ", "), "\n")
} else {
  cat("Every manifest year is represented in the daily files.\n")
}
```

# Section 3 — Metadata timelines and regimes

Two deliberately **separate** concepts — never merged in this notebook:

- **Collection-wide metadata timeline** (product metadata table): every
  footprint-intersecting asset, whether or not it contributed valid
  BAAQMD pixels. Descriptive context for the record as delivered by
  Earth Engine.
- **Scientific daily-regime timeline** (daily audit table): built ONLY
  from the contributor-scoped `contributing_processor_version_set`
  column, so daily scientific values are grouped by the metadata of the
  products that actually produced them — never by non-contributing
  footprint-intersecting products.

**Regime convention (diagnostic only).** A day's *contributor
signature* is its `contributing_processor_version_set` string. A
**contributor processor regime** is a maximal run of consecutive
with-contributor days sharing one signature; days without contributors
carry no signature and neither break nor extend a regime. This is a
descriptive grouping convention for this audit — not a decided
scientific stratification.

## Collection-wide metadata timeline (context only)

```{r collection-timeline, eval = data_available, fig.height = 6}
collection_spans <- products %>%
  group_by(PROCESSOR_VERSION) %>%
  summarise(n_asset_rows = n(),
            first_date = min(local_date),
            last_date = max(local_date), .groups = "drop") %>%
  arrange(first_date)
kable(collection_spans,
      caption = paste("Collection-wide PROCESSOR_VERSION spans (ALL",
                      "footprint-intersecting assets - context only;",
                      "not the scientific daily regimes)."))

timeline_long <- products %>%
  select(local_date, PROCESSOR_VERSION, ALGORITHM_VERSION,
         SPATIAL_RESOLUTION, PROCESSING_STATUS) %>%
  pivot_longer(-local_date, names_to = "field", values_to = "value") %>%
  distinct()
ggplot(timeline_long, aes(x = local_date, y = value)) +
  geom_point(size = 0.4, alpha = 0.5) +
  facet_wrap(~ field, ncol = 1, scales = "free_y") +
  labs(title = paste("Collection-wide metadata timeline (ALL",
                     "footprint-intersecting assets)"),
       subtitle = paste("Context only - includes non-contributing",
                        "products. The scientific daily regimes below",
                        "use contributor-scoped fields. Overlaps and",
                        "gaps are not proof of processing effects."),
       x = "Bay Area local date", y = NULL) +
  theme_minimal(base_size = 10)
```

## Scientific daily-regime timeline (contributor-scoped)

```{r contrib-regimes, eval = data_available}
contrib_days <- daily %>%
  filter(valid_contributor_count > 0) %>%
  arrange(local_date)

# Run-length regimes over the with-contributor day sequence.
runs <- rle(contrib_days$contributing_processor_version_set)
contrib_days$contrib_regime_id <-
  rep(seq_along(runs$lengths), runs$lengths)

contrib_regime_table <- contrib_days %>%
  group_by(contrib_regime_id,
           contrib_signature = contributing_processor_version_set) %>%
  summarise(start_date = min(local_date),
            end_date = max(local_date),
            n_contributor_days = n(), .groups = "drop") %>%
  arrange(start_date) %>%
  mutate(regime_label = paste0("R", contrib_regime_id, ": ",
                               contrib_signature),
         is_mixed_signature =
           str_detect(contrib_signature,
                      fixed(config$set_separator)))
kable(contrib_regime_table,
      caption = paste("Contributor-scoped processor regimes (runs of",
                      "consecutive with-contributor days sharing one",
                      "contributing_processor_version_set signature;",
                      "diagnostic convention only)."))

# Attach the contributor regime to the daily table (NA for days with no
# valid contributors).
daily <- daily %>%
  left_join(contrib_days %>%
              select(local_date, contrib_regime_id),
            by = "local_date") %>%
  left_join(contrib_regime_table %>%
              select(contrib_regime_id, regime_label),
            by = "contrib_regime_id")
```

```{r full-series, eval = data_available}
ggplot(daily, aes(x = local_date, y = regional_mean_no2,
                  color = regime_label)) +
  geom_point(size = 0.4, alpha = 0.6, na.rm = TRUE) +
  scale_y_continuous(labels = label_scientific()) +
  labs(title = paste("Full-history daily BAAQMD area-weighted mean",
                     "satellite NO2 column"),
       subtitle = paste("Colored by contributor-scoped processor",
                        "regime (diagnostic convention). Gaps are",
                        "missing days - never interpolated."),
       x = "Bay Area local date", y = "mol/m²",
       color = "Contributor regime") +
  theme_minimal(base_size = 10) +
  theme(legend.position = "bottom")
```

# Section 4 — Coverage and missingness by contributor regime

```{r coverage-by-regime, eval = data_available}
coverage_by_regime <- daily %>%
  mutate(regime = coalesce(regime_label, "(no contributor regime)")) %>%
  group_by(regime) %>%
  summarise(
    n_days = n(),
    n_valid_days = sum(has_valid_value == 1, na.rm = TRUE),
    pct_valid_days = 100 * n_valid_days / n_days,
    n_no_product_days = sum(daily_distinct_product_count == 0),
    n_products_no_valid = sum(daily_distinct_product_count > 0 &
                                has_valid_value == 0),
    median_valid_fraction_valid_days =
      median(valid_area_fraction[has_valid_value == 1], na.rm = TRUE),
    n_non_nominal_days = sum(has_contributing_non_nominal == 1,
                             na.rm = TRUE),
    .groups = "drop"
  )
kable(coverage_by_regime, digits = 2,
      caption = paste("Coverage and missingness by contributor-scoped",
                      "processor regime. Days without valid",
                      "contributors are grouped as",
                      "'(no contributor regime)'."))
```

```{r monthly-heatmap, eval = data_available, fig.height = 5}
monthly <- daily %>%
  mutate(yr = year(local_date), mo = month(local_date)) %>%
  group_by(yr, mo) %>%
  summarise(pct_valid = 100 * mean(has_valid_value == 1, na.rm = TRUE),
            .groups = "drop")
ggplot(monthly, aes(x = factor(mo), y = factor(yr), fill = pct_valid)) +
  geom_tile(color = "white") +
  scale_fill_viridis_c(limits = c(0, 100)) +
  labs(title = "Monthly coverage: % of days with a valid regional value",
       x = "Calendar month", y = "Year", fill = "% valid days") +
  theme_minimal(base_size = 10)
```

```{r fraction-by-season, eval = data_available, fig.height = 5}
# Season labels are a DESCRIPTIVE grouping convention only (DJF / MAM /
# JJA / SON), not decided methodology.
season_of <- function(m) {
  case_when(m %in% c(12, 1, 2) ~ "DJF",
            m %in% 3:5 ~ "MAM",
            m %in% 6:8 ~ "JJA",
            TRUE ~ "SON")
}
daily <- daily %>%
  mutate(season = factor(season_of(month(local_date)),
                         levels = c("DJF", "MAM", "JJA", "SON")))

ggplot(daily %>% filter(has_valid_value == 1),
       aes(x = season, y = valid_area_fraction)) +
  geom_boxplot(outlier.size = 0.4) +
  facet_wrap(~ coalesce(regime_label, "(no contributor regime)")) +
  labs(title = paste("Valid-area fraction by season and",
                     "contributor-scoped processor regime"),
       subtitle = "Valid days only; no coverage threshold is applied.",
       x = "Season (descriptive convention)",
       y = "Valid-area fraction") +
  theme_minimal(base_size = 10)
```

```{r contributor-distributions, eval = data_available, fig.height = 4}
ggplot(daily,
       aes(x = factor(valid_contributor_count))) +
  geom_bar() +
  facet_wrap(~ coalesce(regime_label, "(no contributor regime)"), scales = "free_y") +
  labs(title = paste("Valid-contributor count per day, by",
                     "contributor-scoped processor regime"),
       subtitle = paste("Contributors are products with actual valid",
                        "BAAQMD pixels - footprint intersection alone",
                        "is not contribution."),
       x = "Valid contributors per day", y = "Days") +
  theme_minimal(base_size = 10)

non_nominal_by_year <- daily %>%
  group_by(yr = year(local_date)) %>%
  summarise(days_with_non_nominal_contributor =
              sum(has_contributing_non_nominal == 1, na.rm = TRUE),
            .groups = "drop")
kable(non_nominal_by_year,
      caption = paste("Days per year with a contributing non-NOMINAL",
                      "product (flagged, retained, never excluded)."))
```

# Section 5 — Season-matched distributions (regime × calendar month)

```{r season-matched, eval = data_available}
season_matched <- daily %>%
  filter(has_valid_value == 1, !is.na(regime_label)) %>%
  group_by(regime_label, mo = month(local_date)) %>%
  summarise(
    n_valid_days = n(),
    median_no2 = median(regional_mean_no2),
    p25 = quantile(regional_mean_no2, 0.25),
    p75 = quantile(regional_mean_no2, 0.75),
    iqr = p75 - p25,
    p10 = quantile(regional_mean_no2, 0.10),
    p90 = quantile(regional_mean_no2, 0.90),
    median_valid_fraction = median(valid_area_fraction),
    .groups = "drop"
  ) %>%
  arrange(mo, regime_label)
kable(season_matched, digits = 8,
      caption = paste("Contributor-scoped regime × calendar-month",
                      "distributions of the daily regional satellite",
                      "NO2 column (mol/m²). Descriptive only -",
                      "differences are confounded by year, meteorology,",
                      "and emissions changes."))
```

# Section 6 — Transition diagnostics

Windows of ±`r config$transition_window_days` days (display convention
only) around each **contributor-scoped** processor-regime change (the
scientific daily-regime timeline of Section 3, not the collection-wide
asset timeline). **These plots and summaries
are descriptive. A shift across a transition is NOT proof of a
retrieval-processing effect** — season, meteorology, emissions trends,
and coverage changes are confounded with every transition date.

```{r transitions, eval = data_available, fig.height = 4}
transitions <- contrib_regime_table %>%
  arrange(start_date) %>%
  mutate(prev_label = lag(regime_label)) %>%
  filter(!is.na(prev_label)) %>%
  select(change_date = start_date, from_regime = prev_label,
         to_regime = regime_label)
kable(transitions,
      caption = "Contributor-scoped processor-regime transition dates.")

w <- config$transition_window_days
for (i in seq_len(nrow(transitions))) {
  tr <- transitions[i, ]
  window_data <- daily %>%
    filter(local_date >= tr$change_date - w,
           local_date < tr$change_date + w)
  p <- ggplot(window_data,
              aes(x = local_date, y = regional_mean_no2,
                  color = coalesce(regime_label, "(no contributor regime)"))) +
    geom_point(size = 0.8, na.rm = TRUE) +
    # Pass the Date itself: a numeric xintercept on a Date scale raises
    # a coercion warning on every transition plot.
    geom_vline(xintercept = tr$change_date, linetype = "dashed") +
    scale_y_continuous(labels = label_scientific()) +
    labs(title = paste0("Transition ", i, ": ", tr$from_regime,
                        " → ", tr$to_regime),
         subtitle = paste("±", w, "days. Descriptive only - not proof",
                          "of a processing effect."),
         x = "Bay Area local date", y = "mol/m²", color = "Regime") +
    theme_minimal(base_size = 10)
  print(p)

  summary_tbl <- window_data %>%
    mutate(side = if_else(local_date < tr$change_date,
                          "before", "after")) %>%
    group_by(side) %>%
    summarise(n_valid = sum(has_valid_value == 1, na.rm = TRUE),
              median_no2 = median(regional_mean_no2, na.rm = TRUE),
              median_valid_fraction =
                median(valid_area_fraction[has_valid_value == 1],
                       na.rm = TRUE),
              .groups = "drop")
  print(kable(summary_tbl, digits = 8,
              caption = paste0("Transition ", i,
                               " window summary (descriptive only; ",
                               "seasonal confounding likely).")))
}
```

# Section 7 — Retrospective baseline-robustness study

This section replaces the earlier single-target baseline-sensitivity
diagnostic, whose live run showed it was too weak to inform the
baseline-restriction question: it evaluated one target month only; its
longest-regime variant drew history from a regime that is historically
irrelevant to recent targets (and often supplies no calendar-matched
history at all); and an exact target-processor pool is frequently
unavailable after processor changes. The study below evaluates the
same accepted exploratory baseline across **all eligible target months
from `r config$retrospective_start_year` onward**.

**Context (project owner).** This study was commissioned under the
owner's policy-level adoption of **Outcome B** (2026-07-19): the Earth
Engine OFFL record is usable for exploratory historical analysis, but
the full 2018–present record must not be treated as unconditionally
homogeneous. At design time the exact baseline restriction was
undecided; this study provided the retrospective evidence for it, and
the owner's final decision and baseline policy — recorded after review
of the accepted full-history report — are in Section 8. Nothing is
selected by this section's computations: no baseline variant, no
coverage threshold, no correction factor, no episode rule. Differences
reported below are **not** attributed to retrieval processing —
season, meteorology, emission trends, and coverage changes remain
plausible confounders throughout.

**Accepted exploratory baseline (script 06, reimplemented here).** For
a target day: pool the non-null daily area-weighted regional means
(mol/m²) of the SAME calendar month in the previous
`r config$historical_years_diagnostic` years — only dates strictly
earlier than the target year; the baseline is the regional historical
median; signed anomaly = target − median; percentile rank =
100 × count(historical ≤ target) ÷ non-null historical count; no
percentage-change metric; nulls stay null and are never interpolated.

**Historical-pool variants (diagnostic conventions only).** All pools
use the target's calendar month and only years earlier than the
target year:

| Variant | Historical pool |
|---|---|
| `prior-three-years` | all valid days from the previous three years (the accepted exploratory default; reference for all comparisons) |
| `prior-one-year` | valid days from year −1 only |
| `prior-year-minus-2` | valid days from year −2 only |
| `prior-year-minus-3` | valid days from year −3 only |
| `target-processor` | prior-three-years days whose contributor processor signature exactly matches the target month's signature |
| `target-algorithm` | prior-three-years days whose contributor algorithm signature exactly matches the target month's signature |

The **prior-years-separate** variant of the study design is the three
single-year rows taken together (`prior-one-year` ≡ year −1, plus
year −2 and year −3): the baseline is calculated independently for
each available prior year in the accepted three-year window instead of
pooling them.

**Signature rules.** A day's processor (algorithm) signature is its
raw contributor-scoped
`contributing_processor_version_set`
(`contributing_algorithm_version_set`) string; matching is **exact
string equality with no version normalization** (script 06's
normalization is a display convention of that script). A target
month's signature is defined from its with-contributor days: if they
span more than one signature the month is reported as **mixed** and
the signature-matched variants are recorded as UNAVAILABLE for that
month — the dominant signature is never chosen silently; if the month
has no with-contributor days it has no signature. Signature-matched
variants are also recorded as unavailable when no historical day
matches; every unavailability carries an explicit reason.

**Eligibility rule.** A target month is eligible when its year is ≥
`r config$retrospective_start_year` and **every calendar day of the
month is present in the daily export** (script 07 exports a row for
every requested day, so this excludes the trailing partial month and
would surface any export gap). Every calendar day of an eligible month
is a target day; days without a valid regional value are retained with
an explicit reason, never silently dropped.

**Window-representation rule.** The exported record begins partway
through its first year, so early target months have structurally
incomplete historical windows even when their pool is non-empty.
`baseline_available` therefore continues to mean a **non-empty
computable pool**, while a separate flag,
`full_requested_year_window`, records whether **every requested prior
year supplied at least one valid same-calendar-month day** (after the
variant's signature filtering, where applicable). Target months whose
prior-three-years REFERENCE window is partial are never discarded:
they are reported as partial-window diagnostics and summarized in a
clearly labeled **SUPPLEMENTAL** set, while **PRIMARY** robustness
summaries include only target months whose reference window contains
all three requested prior years. All dates are derived dynamically
from the exported record — no first-eligible date is hard-coded.

The 90th/10th references are descriptive labels only — never episode
labels. This section measures **robustness of the exploratory
diagnostics to the historical pool** — it does not select a baseline
method.

## Eligible target months and month-level signatures

```{r retro-eligibility, eval = data_available}
n_hist_years <- config$historical_years_diagnostic

month_completeness <- daily %>%
  mutate(target_month = floor_date(local_date, "month")) %>%
  group_by(target_month) %>%
  summarise(n_days_present = n_distinct(local_date), .groups = "drop") %>%
  mutate(n_days_in_month = as.integer(days_in_month(target_month)),
         is_complete = n_days_present == n_days_in_month)

retro_candidate_months <- month_completeness %>%
  filter(year(target_month) >= config$retrospective_start_year)
excluded_months <- retro_candidate_months %>% filter(!is_complete)
eligible_months <- retro_candidate_months %>%
  filter(is_complete) %>%
  pull(target_month)

cat("Candidate months from", config$retrospective_start_year,
    "onward:", nrow(retro_candidate_months),
    "| eligible (every calendar day exported):",
    length(eligible_months),
    "| excluded as incomplete:", nrow(excluded_months), "\n")
if (nrow(excluded_months) > 0) {
  kable(excluded_months,
        caption = paste("Months excluded from the retrospective study",
                        "(incomplete daily coverage in the export -",
                        "typically the trailing partial month)."))
}
```

```{r retro-signatures, eval = data_available}
contributor_days_by_month <- daily %>%
  mutate(target_month = floor_date(local_date, "month")) %>%
  filter(valid_contributor_count > 0) %>%
  group_by(target_month) %>%
  summarise(
    proc_signatures =
      list(sort(unique(contributing_processor_version_set))),
    alg_signatures =
      list(sort(unique(contributing_algorithm_version_set))),
    n_contributor_days = n(),
    .groups = "drop")

month_signature_tbl <- tibble(target_month = eligible_months) %>%
  left_join(contributor_days_by_month, by = "target_month") %>%
  mutate(
    proc_signatures = map(proc_signatures,
                          ~ if (is.null(.x)) character(0) else .x),
    alg_signatures = map(alg_signatures,
                         ~ if (is.null(.x)) character(0) else .x),
    n_contributor_days = replace_na(n_contributor_days, 0L),
    proc_signature_status = case_when(
      lengths(proc_signatures) == 0 ~ "none",
      lengths(proc_signatures) == 1 ~ "unique",
      TRUE ~ "mixed"),
    alg_signature_status = case_when(
      lengths(alg_signatures) == 0 ~ "none",
      lengths(alg_signatures) == 1 ~ "unique",
      TRUE ~ "mixed"),
    proc_signature_display = map_chr(proc_signatures, paste,
                                     collapse = " | "),
    alg_signature_display = map_chr(alg_signatures, paste,
                                    collapse = " | "))

kable(month_signature_tbl %>%
        count(proc_signature_status, alg_signature_status),
      caption = paste("Eligible target months by month-level",
                      "contributor-signature status. 'mixed' months",
                      "are reported as such; their signature-matched",
                      "variants are unavailable - no dominant",
                      "signature is ever chosen."))

mixed_or_none_months <- month_signature_tbl %>%
  filter(proc_signature_status != "unique" |
           alg_signature_status != "unique") %>%
  select(target_month, proc_signature_status, proc_signature_display,
         alg_signature_status, alg_signature_display)
if (nrow(mixed_or_none_months) > 0) {
  kable(mixed_or_none_months,
        caption = paste("Eligible target months whose processor or",
                        "algorithm signature is mixed or absent (raw",
                        "contributor-scoped set strings)."))
} else {
  cat("Every eligible target month has unique contributor",
      "signatures.\n")
}
```

## Variant baselines for every retrospective target day

Historical pools depend only on the target month (never on the target
day), so pools are built once per month × variant and then joined to
every target day. For every variant × target day the table retains:
historical sample size, historical median, signed anomaly, percentile
rank, availability and its reason, the target day's valid-area
fraction, and the target's processor and algorithm signatures (day-
and month-level). Each month × variant row additionally records its
requested prior years and their representation:
`requested_prior_year_count`, `prior_year_labels_requested`,
`prior_year_labels_with_valid_values`,
`prior_year_count_with_valid_values`, `missing_prior_year_labels`,
`full_requested_year_window`, and the valid historical day count by
source year (`hist_n_by_source_year`). For the signature-matched
variants these are computed AFTER signature filtering, and they are
`NA` when the pool cannot be formed at all (mixed or absent month
signature).

```{r retro-variants, eval = data_available}
valid_daily_retro <- daily %>%
  filter(has_valid_value == 1) %>%
  mutate(mo = month(local_date), yr = year(local_date))

variant_levels <- c("prior-three-years", "prior-one-year",
                    "prior-year-minus-2", "prior-year-minus-3",
                    "target-processor", "target-algorithm")

month_variant_pools <-
  map_dfr(seq_len(nrow(month_signature_tbl)), function(i) {
    msig <- month_signature_tbl[i, ]
    tm <- msig$target_month
    m <- month(tm)
    ty <- year(tm)
    base_pool <- valid_daily_retro %>%
      filter(mo == m, yr >= ty - n_hist_years, yr <= ty - 1)

    # `formed = FALSE` marks signature pools that cannot be formed at
    # all (mixed or absent month signature): their representation
    # fields are NA rather than a misleading "all years missing".
    spec <- function(variant, requested_years, pool, formed,
                     available, reason) {
      represented <- if (formed) sort(unique(pool$yr)) else integer(0)
      missing_years <- setdiff(requested_years, represented)
      per_year_counts <- vapply(requested_years,
                                function(y) sum(pool$yr == y),
                                integer(1))
      tibble(
        target_month = tm, variant = variant,
        hist_values = list(pool$regional_mean_no2),
        hist_n = nrow(pool),
        baseline_available = available, baseline_reason = reason,
        requested_prior_year_count = length(requested_years),
        prior_year_labels_requested =
          paste(requested_years, collapse = " | "),
        prior_year_labels_with_valid_values =
          if (formed) paste(represented, collapse = " | ") else
            NA_character_,
        prior_year_count_with_valid_values =
          if (formed) length(represented) else NA_integer_,
        missing_prior_year_labels =
          if (formed) paste(missing_years, collapse = " | ") else
            NA_character_,
        full_requested_year_window =
          if (formed) length(missing_years) == 0 else NA,
        hist_n_by_source_year =
          if (formed) {
            paste(paste0(requested_years, ":", per_year_counts),
                  collapse = " | ")
          } else {
            NA_character_
          })
    }
    pooled_spec <- function(variant, requested_years, pool,
                            empty_reason) {
      spec(variant, requested_years, pool, formed = TRUE,
           available = nrow(pool) > 0,
           reason = if (nrow(pool) > 0) "ok" else empty_reason)
    }
    signature_spec <- function(variant, status, signatures, column) {
      requested_years <- (ty - n_hist_years):(ty - 1)
      if (status == "none") {
        spec(variant, requested_years, base_pool[0, ], formed = FALSE,
             available = FALSE,
             reason = "target month has no days with valid contributors")
      } else if (status == "mixed") {
        spec(variant, requested_years, base_pool[0, ], formed = FALSE,
             available = FALSE,
             reason = paste0("target month mixed signatures: ",
                             paste(signatures, collapse = " | ")))
      } else {
        pooled_spec(variant, requested_years,
                    base_pool %>%
                      filter(.data[[column]] == signatures[[1]]),
                    paste("no signature-matched valid days in the",
                          "previous three years"))
      }
    }

    bind_rows(
      pooled_spec("prior-three-years", (ty - n_hist_years):(ty - 1),
                  base_pool,
                  paste("no valid same-calendar-month days in the",
                        "previous three years")),
      pooled_spec("prior-one-year", ty - 1,
                  filter(base_pool, yr == ty - 1),
                  "no valid same-calendar-month days in year -1"),
      pooled_spec("prior-year-minus-2", ty - 2,
                  filter(base_pool, yr == ty - 2),
                  "no valid same-calendar-month days in year -2"),
      pooled_spec("prior-year-minus-3", ty - 3,
                  filter(base_pool, yr == ty - 3),
                  "no valid same-calendar-month days in year -3"),
      signature_spec("target-processor", msig$proc_signature_status,
                     msig$proc_signatures[[1]],
                     "contributing_processor_version_set"),
      signature_spec("target-algorithm", msig$alg_signature_status,
                     msig$alg_signatures[[1]],
                     "contributing_algorithm_version_set")
    )
  }) %>%
  mutate(hist_median = map_dbl(hist_values, ~ if (length(.x) > 0) {
           median(.x)
         } else {
           NA_real_
         }),
         hist_small_sample_flag = baseline_available &
           hist_n < config$small_sample_flag_n)

retro_target_days <- daily %>%
  mutate(target_month = floor_date(local_date, "month")) %>%
  filter(target_month %in% eligible_months) %>%
  transmute(
    target_month, local_date, season,
    target_mean = regional_mean_no2,
    target_valid_area_fraction = valid_area_fraction,
    target_day_processor_signature =
      na_if(contributing_processor_version_set, ""),
    target_day_algorithm_signature =
      na_if(contributing_algorithm_version_set, "")) %>%
  left_join(month_signature_tbl %>%
              select(target_month,
                     target_month_processor_status =
                       proc_signature_status,
                     target_month_processor_signatures =
                       proc_signature_display,
                     target_month_algorithm_status =
                       alg_signature_status,
                     target_month_algorithm_signatures =
                       alg_signature_display),
            by = "target_month")

retro_results <- month_variant_pools %>%
  inner_join(retro_target_days, by = "target_month",
             relationship = "many-to-many") %>%
  mutate(
    signed_anomaly = if_else(baseline_available & !is.na(target_mean),
                             target_mean - hist_median, NA_real_),
    percentile_rank = pmap_dbl(
      list(hist_values, target_mean, baseline_available),
      function(h, t, available) {
        if (!available || is.na(t)) return(NA_real_)
        100 * sum(h <= t) / length(h)
      }),
    result_reason = case_when(
      !baseline_available ~ baseline_reason,
      is.na(target_mean) ~ "target day has no valid regional value",
      TRUE ~ "ok"),
    variant = factor(variant, levels = variant_levels)) %>%
  select(-hist_values) %>%
  arrange(local_date, variant)

cat("Retrospective evaluation:", length(eligible_months),
    "target months,", nrow(retro_target_days), "target days,",
    length(variant_levels), "variants,", nrow(retro_results),
    "variant x day rows (all retained in `retro_results`).\n")

kable(retro_results %>%
        filter(local_date == min(local_date)) %>%
        select(variant, local_date, target_mean, hist_n, hist_median,
               signed_anomaly, percentile_rank,
               full_requested_year_window, hist_n_by_source_year,
               result_reason),
      digits = 8,
      caption = paste("Example: all variant rows for the first",
                      "retrospective target day. The full per-day",
                      "table additionally retains the valid-area",
                      "fraction, the day- and month-level signature",
                      "columns, the remaining prior-year",
                      "representation fields, and the small-sample",
                      "display flag."))
```

## Prior-year window representation (full vs partial)

A **non-empty pool** (`baseline_available`) is deliberately distinct
from a **fully represented window** (`full_requested_year_window`):
the pool can be computable while one or more requested prior years
supplied no valid same-calendar-month day at all, because the exported
record begins partway through its first year. Partial-window target
months are retained as diagnostics below and summarized in the
SUPPLEMENTAL sets — never discarded, and never presented as equivalent
to the full three-year baseline.

```{r retro-windows, eval = data_available}
window_by_variant <- month_variant_pools %>%
  mutate(variant = factor(variant, levels = variant_levels)) %>%
  group_by(variant) %>%
  summarise(n_target_months = n(),
            n_full_window = sum(full_requested_year_window %in% TRUE),
            n_partial_window =
              sum(full_requested_year_window %in% FALSE),
            n_pool_not_formed =
              sum(is.na(full_requested_year_window)),
            .groups = "drop")
kable(window_by_variant,
      caption = paste("Requested-window representation by variant.",
                      "'partial' = pool formable but at least one",
                      "requested prior year supplied no valid day",
                      "(after signature filtering, where applicable);",
                      "'not formed' = signature pool not formable",
                      "(mixed or absent month signature)."))

reference_windows <- month_variant_pools %>%
  filter(variant == "prior-three-years") %>%
  select(target_month, requested_prior_year_count,
         prior_year_labels_requested,
         prior_year_labels_with_valid_values,
         prior_year_count_with_valid_values,
         missing_prior_year_labels, full_requested_year_window,
         hist_n, hist_n_by_source_year)

# Classification used by every PRIMARY / SUPPLEMENTAL split below:
# the REFERENCE (prior-three-years) window status of the target month.
reference_window_tbl <- reference_windows %>%
  transmute(target_month,
            reference_window = factor(
              if_else(full_requested_year_window,
                      "full three-year window", "partial window"),
              levels = c("full three-year window", "partial window")))

cat("Prior-three-years REFERENCE windows:",
    sum(reference_windows$full_requested_year_window),
    "target months with all three requested prior years represented;",
    sum(!reference_windows$full_requested_year_window),
    "structurally partial (retained; summarized separately).\n")

partial_window_diagnostics <- reference_windows %>%
  filter(!full_requested_year_window) %>%
  select(target_month, prior_year_labels_with_valid_values,
         missing_prior_year_labels, hist_n, hist_n_by_source_year)
if (nrow(partial_window_diagnostics) > 0) {
  kable(partial_window_diagnostics,
        caption = paste("Partial-window diagnostics: eligible target",
                        "months whose prior-three-years reference",
                        "window is structurally incomplete because",
                        "the exported record does not cover every",
                        "requested prior year. Retained - excluded",
                        "from PRIMARY summaries and reported in the",
                        "SUPPLEMENTAL set."))
} else {
  cat("Every eligible target month has a full three-year reference",
      "window.\n")
}

first_full_window <- reference_windows %>%
  filter(full_requested_year_window) %>%
  group_by(calendar_month = month(target_month)) %>%
  summarise(first_full_window_target_month = min(target_month),
            .groups = "drop") %>%
  right_join(tibble(calendar_month = 1:12),
             by = "calendar_month") %>%
  arrange(calendar_month)
kable(first_full_window,
      caption = paste("First target month with a full three-year",
                      "reference window, per calendar month (derived",
                      "from the exported record; NA = never achieved",
                      "in the exported range)."))
```

## Availability of signature-matched baselines

```{r retro-availability, eval = data_available}
availability_summary <- retro_results %>%
  group_by(variant) %>%
  summarise(
    n_target_days = n(),
    n_baseline_available = sum(baseline_available),
    pct_baseline_unavailable = 100 * mean(!baseline_available),
    n_anomaly_computed = sum(!is.na(percentile_rank)),
    median_hist_n_when_available = median(hist_n[baseline_available]),
    n_small_sample_days = sum(hist_small_sample_flag),
    .groups = "drop")
kable(availability_summary, digits = 1,
      caption = paste("Availability per variant.",
                      "pct_baseline_unavailable is the percentage of",
                      "target days whose historical pool could not be",
                      "formed; anomalies additionally require a valid",
                      "target day. The small-sample flag is a display",
                      "convention, not a threshold."))

reason_breakdown <- retro_results %>%
  mutate(reason_class = if_else(
    str_starts(result_reason, "target month mixed signatures"),
    "target month mixed signatures (variant unavailable)",
    result_reason)) %>%
  count(variant, reason_class) %>%
  pivot_wider(names_from = variant, values_from = n,
              values_fill = 0)
kable(reason_breakdown,
      caption = paste("Target-day counts by result reason and",
                      "variant (mixed-signature reasons grouped for",
                      "display; the per-day table keeps the full",
                      "signature lists)."))

signature_month_availability <- month_variant_pools %>%
  filter(variant %in% c("target-processor", "target-algorithm")) %>%
  group_by(variant) %>%
  summarise(n_target_months = n(),
            n_months_available = sum(baseline_available),
            pct_months_unavailable = 100 * mean(!baseline_available),
            .groups = "drop")
kable(signature_month_availability, digits = 1,
      caption = paste("Month-level availability of the",
                      "signature-matched variants."))

signature_unavailability_by_year <- retro_results %>%
  filter(variant %in% c("target-processor", "target-algorithm")) %>%
  group_by(variant, target_year = year(local_date)) %>%
  summarise(pct_days_unavailable = 100 * mean(!baseline_available),
            .groups = "drop") %>%
  pivot_wider(names_from = variant,
              values_from = pct_days_unavailable)
kable(signature_unavailability_by_year, digits = 1,
      caption = paste("Percentage of target days with an unavailable",
                      "signature-matched baseline, by target year."))
```

## Robustness relative to the prior-three-years reference

All comparisons below use `prior-three-years` (the accepted
exploratory default) as the reference and are **conditional on
availability**: a variant is compared only on days where both it and
the reference produce a value. Sign agreement uses exact `sign()`
equality (an exact-zero anomaly would count as its own category).
Every summary is reported in two sets: **PRIMARY** (target months
whose reference window contains all three requested prior years) and
**SUPPLEMENTAL** (partial-window months — structurally incomplete and
not directly equivalent to the full three-year baseline).

```{r retro-agreement, eval = data_available}
reference_variant <- "prior-three-years"
reference_tbl <- retro_results %>%
  filter(variant == reference_variant) %>%
  select(local_date, ref_anomaly = signed_anomaly,
         ref_pct = percentile_rank)

comparison <- retro_results %>%
  filter(variant != reference_variant) %>%
  inner_join(reference_tbl, by = "local_date") %>%
  filter(!is.na(percentile_rank), !is.na(ref_pct)) %>%
  left_join(reference_window_tbl, by = "target_month") %>%
  mutate(abs_pct_diff = abs(percentile_rank - ref_pct),
         sign_agrees = sign(signed_anomaly) == sign(ref_anomaly))

comparison_primary <- comparison %>%
  filter(reference_window == "full three-year window")
comparison_supplemental <- comparison %>%
  filter(reference_window == "partial window")
cat("Comparable variant x day rows - PRIMARY (full reference",
    "window):", nrow(comparison_primary),
    "| SUPPLEMENTAL (partial reference window):",
    nrow(comparison_supplemental), "\n")

summarise_agreement <- function(df) {
  df %>%
    group_by(variant) %>%
    summarise(n_days_compared = n(),
              pct_sign_agreement = 100 * mean(sign_agrees),
              n_sign_disagreements = sum(!sign_agrees),
              median_abs_pct_diff = median(abs_pct_diff),
              max_abs_pct_diff = max(abs_pct_diff),
              .groups = "drop")
}
kable(summarise_agreement(comparison_primary), digits = 1,
      caption = paste("PRIMARY - anomaly-sign agreement and",
                      "percentile-rank differences vs the",
                      "prior-three-years reference (full",
                      "three-year reference windows only)."))
kable(summarise_agreement(comparison_supplemental), digits = 1,
      caption = paste("SUPPLEMENTAL - same metrics for the",
                      "partial-window target months (one or two",
                      "represented prior years): structurally",
                      "incomplete, not directly equivalent to the",
                      "full three-year baseline."))
```

```{r retro-tails, eval = data_available}
summarise_tails <- function(df) {
  df %>%
    group_by(variant) %>%
    summarise(
      n_ref_gt90 = sum(ref_pct > 90),
      n_variant_gt90 = sum(percentile_rank > 90),
      n_both_gt90 = sum(ref_pct > 90 & percentile_rank > 90),
      jaccard_gt90 = if_else(
        n_ref_gt90 + n_variant_gt90 - n_both_gt90 > 0,
        n_both_gt90 / (n_ref_gt90 + n_variant_gt90 - n_both_gt90),
        NA_real_),
      n_ref_lt10 = sum(ref_pct < 10),
      n_variant_lt10 = sum(percentile_rank < 10),
      n_both_lt10 = sum(ref_pct < 10 & percentile_rank < 10),
      jaccard_lt10 = if_else(
        n_ref_lt10 + n_variant_lt10 - n_both_lt10 > 0,
        n_both_lt10 / (n_ref_lt10 + n_variant_lt10 - n_both_lt10),
        NA_real_),
      .groups = "drop")
}
kable(summarise_tails(comparison_primary), digits = 2,
      caption = paste("PRIMARY - overlap of DESCRIPTIVE >90th and",
                      "<10th percentile dates with the reference",
                      "(Jaccard = shared / union; NA when neither",
                      "side has such days). Full three-year",
                      "reference windows only. Descriptive",
                      "references - never episode labels."))
kable(summarise_tails(comparison_supplemental), digits = 2,
      caption = paste("SUPPLEMENTAL - same overlap metrics for the",
                      "structurally incomplete partial-window",
                      "target months."))
```

## Robustness by calendar month and descriptive season

```{r retro-by-month, eval = data_available, fig.height = 6}
agreement_by_month <- comparison %>%
  mutate(mo = month(local_date)) %>%
  group_by(reference_window, variant, mo) %>%
  summarise(n_days_compared = n(),
            pct_sign_agreement = 100 * mean(sign_agrees),
            median_abs_pct_diff = median(abs_pct_diff),
            .groups = "drop")

month_pivot <- function(df, value_col) {
  df %>%
    select(mo, variant, all_of(value_col)) %>%
    pivot_wider(names_from = variant,
                values_from = all_of(value_col))
}
by_month_primary <- agreement_by_month %>%
  filter(reference_window == "full three-year window")
by_month_supplemental <- agreement_by_month %>%
  filter(reference_window == "partial window")

kable(month_pivot(by_month_primary, "median_abs_pct_diff"),
      digits = 1,
      caption = paste("PRIMARY - median |percentile-rank difference|",
                      "vs the reference, by calendar month (full",
                      "three-year reference windows only)."))
kable(month_pivot(by_month_primary, "pct_sign_agreement"),
      digits = 1,
      caption = paste("PRIMARY - anomaly-sign agreement (%) vs the",
                      "reference, by calendar month."))
kable(month_pivot(by_month_supplemental, "median_abs_pct_diff"),
      digits = 1,
      caption = paste("SUPPLEMENTAL - median |percentile-rank",
                      "difference| by calendar month for the",
                      "structurally incomplete partial-window",
                      "months."))
kable(month_pivot(by_month_supplemental, "pct_sign_agreement"),
      digits = 1,
      caption = paste("SUPPLEMENTAL - anomaly-sign agreement (%) by",
                      "calendar month for the partial-window",
                      "months."))

ggplot(agreement_by_month,
       aes(x = factor(mo), y = variant,
           fill = median_abs_pct_diff)) +
  geom_tile(color = "white") +
  scale_fill_viridis_c() +
  facet_wrap(~ reference_window, ncol = 1) +
  labs(title = paste("Median |percentile-rank difference| vs the",
                     "prior-three-years reference"),
       subtitle = paste("Conditional on availability; cells without",
                        "comparable days are blank. Partial-window",
                        "panel is structurally incomplete."),
       x = "Calendar month", y = NULL,
       fill = "Median |Δ percentile|") +
  theme_minimal(base_size = 10)
```

```{r retro-by-season, eval = data_available}
agreement_by_season <- comparison %>%
  group_by(reference_window, variant, season) %>%
  summarise(n_days_compared = n(),
            pct_sign_agreement = 100 * mean(sign_agrees),
            median_abs_pct_diff = median(abs_pct_diff),
            max_abs_pct_diff = max(abs_pct_diff),
            .groups = "drop")
kable(agreement_by_season %>%
        filter(reference_window == "full three-year window") %>%
        select(-reference_window),
      digits = 1,
      caption = paste("PRIMARY - robustness metrics by descriptive",
                      "season (DJF/MAM/JJA/SON display convention;",
                      "full three-year reference windows only)."))
kable(agreement_by_season %>%
        filter(reference_window == "partial window") %>%
        select(-reference_window),
      digits = 1,
      caption = paste("SUPPLEMENTAL - robustness metrics by",
                      "descriptive season for the structurally",
                      "incomplete partial-window months."))
```

## Robustness by processor-transition period

Transition periods are the merged ±`r config$transition_window_days`-day
windows (display convention) around the contributor-scoped
processor-regime transition dates of Section 6. **In-period vs
out-of-period differences are confounded with season** — transitions
cluster in particular calendar months — and are never proof of a
processing effect.

```{r retro-transitions, eval = data_available}
w <- config$transition_window_days
transition_windows <- transitions %>%
  arrange(change_date) %>%
  mutate(win_start = change_date - w, win_end = change_date + w)

periods <- list()
current <- NULL
for (i in seq_len(nrow(transition_windows))) {
  row <- transition_windows[i, ]
  if (is.null(current) || row$win_start > current$period_end) {
    if (!is.null(current)) periods[[length(periods) + 1]] <- current
    current <- tibble(period_start = row$win_start,
                      period_end = row$win_end,
                      n_transitions = 1L)
  } else {
    current$period_end <- max(current$period_end, row$win_end)
    current$n_transitions <- current$n_transitions + 1L
  }
}
if (!is.null(current)) periods[[length(periods) + 1]] <- current
transition_periods <- bind_rows(periods) %>%
  mutate(period_id = row_number(), .before = 1)
kable(transition_periods,
      caption = paste("Merged transition periods (overlapping ±", w,
                      "-day windows around contributor-regime",
                      "transitions are combined)."))

date_transition_flag <- retro_target_days %>%
  distinct(local_date) %>%
  mutate(in_transition_period = map_lgl(local_date, function(d) {
    any(transition_periods$period_start <= d &
          d <= transition_periods$period_end)
  }))

transition_agreement <- comparison %>%
  left_join(date_transition_flag, by = "local_date") %>%
  group_by(reference_window, variant, in_transition_period) %>%
  summarise(n_days_compared = n(),
            pct_sign_agreement = 100 * mean(sign_agrees),
            median_abs_pct_diff = median(abs_pct_diff),
            max_abs_pct_diff = max(abs_pct_diff),
            .groups = "drop")
kable(transition_agreement %>%
        filter(reference_window == "full three-year window") %>%
        select(-reference_window),
      digits = 1,
      caption = paste("PRIMARY - robustness metrics inside vs",
                      "outside transition periods (full three-year",
                      "reference windows only; descriptive only;",
                      "seasonally confounded)."))
kable(transition_agreement %>%
        filter(reference_window == "partial window") %>%
        select(-reference_window),
      digits = 1,
      caption = paste("SUPPLEMENTAL - same metrics for the",
                      "structurally incomplete partial-window",
                      "months (descriptive only; seasonally",
                      "confounded)."))

transition_availability <- retro_results %>%
  left_join(date_transition_flag, by = "local_date") %>%
  filter(variant %in% c("target-processor", "target-algorithm")) %>%
  group_by(variant, in_transition_period) %>%
  summarise(n_target_days = n(),
            pct_baseline_unavailable =
              100 * mean(!baseline_available),
            .groups = "drop")
kable(transition_availability, digits = 1,
      caption = paste("Unavailability of signature-matched baselines",
                      "inside vs outside transition periods."))
```

## Coverage sensitivity for the prior-three-years baseline (candidates only)

The coverage values below are **sensitivity candidates only — none is
an adopted threshold**. Each candidate filters BOTH the historical
pool and the target day by the day's valid-area fraction
("any-valid" = every day with a valid regional value, i.e. no
coverage filter, matching the accepted exploratory rule). Under a
candidate filter, a prior year counts as **represented only when at
least one historical day from that source year survives the filter**,
so raising the candidate can change a target month from a full
three-year window to a partial one — such changes are reported below,
never applied silently. Every target-month-based coverage summary
below is split into PRIMARY and SUPPLEMENTAL sets using the same
reference classification as the rest of Section 7 — the target
month's any-valid prior-three-years reference window (that pool is
the reference pool by construction). Only the whole-export seasonal
retention table remains global: it is a contextual sampling
diagnostic over all valid days in the export, not defined over
retrospective target months.

```{r coverage-sensitivity, eval = data_available, fig.height = 5}
coverage_candidates <- tibble(
  min_fraction = config$coverage_candidates,
  candidate = if_else(config$coverage_candidates == 0, "any-valid",
                      paste0(">=", format(config$coverage_candidates,
                                          nsmall = 2))))

coverage_month_windows <-
  map_dfr(seq_len(nrow(coverage_candidates)), function(ci) {
    cand_label <- coverage_candidates$candidate[[ci]]
    min_fraction <- coverage_candidates$min_fraction[[ci]]
    map_dfr(eligible_months, function(tm) {
      m <- month(tm)
      ty <- year(tm)
      requested_years <- (ty - n_hist_years):(ty - 1)
      hist_pool <- valid_daily_retro %>%
        filter(mo == m, yr >= ty - n_hist_years, yr <= ty - 1,
               valid_area_fraction >= min_fraction)
      represented <- sort(unique(hist_pool$yr))
      tibble(candidate = cand_label, target_month = tm,
             hist_values = list(hist_pool$regional_mean_no2),
             hist_n = nrow(hist_pool),
             hist_median = if (nrow(hist_pool) > 0) {
               median(hist_pool$regional_mean_no2)
             } else {
               NA_real_
             },
             prior_year_count_with_valid_values =
               length(represented),
             missing_prior_year_labels =
               paste(setdiff(requested_years, represented),
                     collapse = " | "),
             full_requested_year_window =
               length(setdiff(requested_years, represented)) == 0,
             hist_n_by_source_year =
               paste(paste0(requested_years, ":",
                            vapply(requested_years,
                                   function(y) sum(hist_pool$yr == y),
                                   integer(1))),
                     collapse = " | "))
    })
  }) %>%
  mutate(candidate = factor(candidate,
                            levels = coverage_candidates$candidate)) %>%
  left_join(reference_window_tbl, by = "target_month")

coverage_results <- coverage_month_windows %>%
  select(candidate, target_month, reference_window, hist_values,
         hist_n, hist_median) %>%
  inner_join(retro_target_days, by = "target_month",
             relationship = "many-to-many") %>%
  mutate(
    min_fraction =
      coverage_candidates$min_fraction[as.integer(candidate)],
    target_retained = !is.na(target_mean) &
      target_valid_area_fraction >= min_fraction,
    signed_anomaly = if_else(target_retained & hist_n > 0,
                             target_mean - hist_median, NA_real_),
    percentile_rank = pmap_dbl(
      list(hist_values, target_mean, target_retained),
      function(h, t, retained) {
        if (!retained || length(h) == 0) return(NA_real_)
        100 * sum(h <= t) / length(h)
      })) %>%
  select(-hist_values, -min_fraction)

cat("Coverage candidate x day rows - PRIMARY (full reference",
    "window):",
    sum(coverage_results$reference_window ==
          "full three-year window"),
    "| SUPPLEMENTAL (partial reference window):",
    sum(coverage_results$reference_window == "partial window"), "\n")

coverage_target_summary <- coverage_results %>%
  group_by(reference_window, candidate) %>%
  summarise(n_target_days = n(),
            n_target_days_retained = sum(target_retained),
            pct_target_days_retained = 100 * mean(target_retained),
            n_anomaly_computed = sum(!is.na(percentile_rank)),
            .groups = "drop")
kable(coverage_target_summary %>%
        filter(reference_window == "full three-year window") %>%
        select(-reference_window),
      digits = 1,
      caption = paste("PRIMARY - target-day retention per coverage",
                      "candidate (full three-year reference windows",
                      "only; sensitivity candidates only)."))
kable(coverage_target_summary %>%
        filter(reference_window == "partial window") %>%
        select(-reference_window),
      digits = 1,
      caption = paste("SUPPLEMENTAL - target-day retention per",
                      "coverage candidate for the structurally",
                      "incomplete partial-window months."))

any_valid_windows <- coverage_month_windows %>%
  filter(candidate == "any-valid") %>%
  select(target_month,
         any_valid_full_window = full_requested_year_window,
         any_valid_year_count = prior_year_count_with_valid_values)
# For the any-valid rows the two change metrics are zero by
# construction (the candidate IS the comparison pool).
coverage_month_windows_vs_any_valid <- coverage_month_windows %>%
  left_join(any_valid_windows, by = "target_month") %>%
  mutate(lost_source_year = prior_year_count_with_valid_values <
           any_valid_year_count,
         full_to_partial = any_valid_full_window &
           !full_requested_year_window)

coverage_pool_summary <- coverage_month_windows_vs_any_valid %>%
  group_by(reference_window, candidate) %>%
  summarise(n_target_months = n(),
            median_hist_n_per_month = median(hist_n),
            min_hist_n = min(hist_n),
            n_months_empty_pool = sum(hist_n == 0),
            n_months_full_window = sum(full_requested_year_window),
            n_months_partial_window =
              sum(!full_requested_year_window),
            n_months_losing_a_source_year = sum(lost_source_year),
            n_months_full_to_partial = sum(full_to_partial),
            .groups = "drop")
kable(coverage_pool_summary %>%
        filter(reference_window == "full three-year window") %>%
        select(-reference_window),
      digits = 1,
      caption = paste("PRIMARY - historical prior-three-years pool",
                      "sizes, candidate-specific window",
                      "representation, and source-year changes vs",
                      "the any-valid pool, for target months with a",
                      "full any-valid reference window (a source",
                      "year counts as represented only when at least",
                      "one of its days survives the candidate",
                      "filter)."))
kable(coverage_pool_summary %>%
        filter(reference_window == "partial window") %>%
        select(-reference_window),
      digits = 1,
      caption = paste("SUPPLEMENTAL - same pool and window metrics",
                      "for the structurally incomplete",
                      "partial-window target months."))

demoted_months <- coverage_month_windows_vs_any_valid %>%
  filter(candidate != "any-valid", full_to_partial) %>%
  select(reference_window, candidate, target_month,
         missing_prior_year_labels, hist_n_by_source_year)
if (nrow(demoted_months) > 0) {
  kable(demoted_months,
        caption = paste("Target months whose reference window",
                        "changes from full to partial under a",
                        "candidate coverage filter (reported, never",
                        "silently applied)."))
} else {
  cat("No candidate coverage filter changes any full three-year",
      "window to a partial window.\n")
}

historical_retention_by_season <-
  map_dfr(seq_len(nrow(coverage_candidates)), function(ci) {
    valid_daily_retro %>%
      filter(valid_area_fraction >=
               coverage_candidates$min_fraction[[ci]]) %>%
      count(season, name = "n_valid_days_retained") %>%
      mutate(candidate = coverage_candidates$candidate[[ci]])
  }) %>%
  pivot_wider(names_from = season,
              values_from = n_valid_days_retained, values_fill = 0)
kable(historical_retention_by_season,
      caption = paste("Valid days retained across the WHOLE export,",
                      "by season and coverage candidate. GLOBAL",
                      "contextual sampling diagnostic over all valid",
                      "days in the export - not defined over",
                      "retrospective target months, hence",
                      "deliberately not split into PRIMARY /",
                      "SUPPLEMENTAL sets."))

pool_size_plot <- function(df, title_prefix, subtitle_note) {
  ggplot(df %>% mutate(mo = month(target_month)),
         aes(x = factor(mo), y = hist_n)) +
    geom_boxplot(outlier.size = 0.4) +
    facet_wrap(~ candidate) +
    labs(title = paste(title_prefix, "- historical-pool size per",
                       "target month, by coverage candidate"),
         subtitle = subtitle_note,
         x = "Calendar month of target",
         y = "Historical days in pool") +
    theme_minimal(base_size = 10)
}
pool_size_plot(
  coverage_month_windows %>%
    filter(reference_window == "full three-year window"),
  "PRIMARY",
  paste("Full three-year reference windows only.",
        "Prior-three-years pools; sensitivity candidates -",
        "no threshold is adopted."))
pool_size_plot(
  coverage_month_windows %>%
    filter(reference_window == "partial window"),
  "SUPPLEMENTAL",
  paste("Structurally incomplete partial-window target months -",
        "not directly equivalent to the full three-year baseline.",
        "Prior-three-years pools; sensitivity candidates -",
        "no threshold is adopted."))
```

```{r coverage-comparison, eval = data_available}
coverage_reference <- coverage_results %>%
  filter(candidate == "any-valid") %>%
  select(local_date, ref_pct = percentile_rank,
         ref_anomaly = signed_anomaly)

# coverage_results already carries reference_window (joined from
# reference_window_tbl above), so no re-join is needed here.
coverage_comparison <- coverage_results %>%
  filter(candidate != "any-valid") %>%
  inner_join(coverage_reference, by = "local_date") %>%
  filter(!is.na(percentile_rank), !is.na(ref_pct)) %>%
  mutate(abs_pct_diff = abs(percentile_rank - ref_pct),
         sign_agrees = sign(signed_anomaly) == sign(ref_anomaly))

coverage_primary <- coverage_comparison %>%
  filter(reference_window == "full three-year window")
coverage_supplemental <- coverage_comparison %>%
  filter(reference_window == "partial window")
cat("Comparable candidate x day rows - PRIMARY (full reference",
    "window):", nrow(coverage_primary),
    "| SUPPLEMENTAL (partial reference window):",
    nrow(coverage_supplemental), "\n")

summarise_coverage <- function(df) {
  df %>%
    group_by(candidate) %>%
    summarise(n_days_compared = n(),
              n_sign_changes = sum(!sign_agrees),
              pct_sign_agreement = 100 * mean(sign_agrees),
              median_abs_pct_diff = median(abs_pct_diff),
              max_abs_pct_diff = max(abs_pct_diff),
              .groups = "drop")
}
kable(summarise_coverage(coverage_primary), digits = 1,
      caption = paste("PRIMARY - percentile-rank and anomaly-sign",
                      "changes vs the any-valid reference (days",
                      "retained under both; full three-year",
                      "reference windows only; sensitivity",
                      "candidates only)."))
kable(summarise_coverage(coverage_supplemental), digits = 1,
      caption = paste("SUPPLEMENTAL - same metrics for the",
                      "structurally incomplete partial-window",
                      "target months."))

coverage_retention_by_season <- coverage_results %>%
  group_by(reference_window, candidate, season) %>%
  summarise(pct_target_days_retained = 100 * mean(target_retained),
            .groups = "drop") %>%
  pivot_wider(names_from = season,
              values_from = pct_target_days_retained)
kable(coverage_retention_by_season %>%
        filter(reference_window == "full three-year window") %>%
        select(-reference_window),
      digits = 1,
      caption = paste("PRIMARY - percentage of target days retained",
                      "by season and coverage candidate (full",
                      "three-year reference windows only; seasonal",
                      "sampling effect)."))
kable(coverage_retention_by_season %>%
        filter(reference_window == "partial window") %>%
        select(-reference_window),
      digits = 1,
      caption = paste("SUPPLEMENTAL - percentage of target days",
                      "retained by season for the structurally",
                      "incomplete partial-window months."))

coverage_comparison_by_season <- coverage_comparison %>%
  group_by(reference_window, candidate, season) %>%
  summarise(n_days_compared = n(),
            median_abs_pct_diff = median(abs_pct_diff),
            n_sign_changes = sum(!sign_agrees),
            .groups = "drop")
kable(coverage_comparison_by_season %>%
        filter(reference_window == "full three-year window") %>%
        select(-reference_window),
      digits = 1,
      caption = paste("PRIMARY - rank and sign changes vs the",
                      "any-valid reference, by season and coverage",
                      "candidate."))
kable(coverage_comparison_by_season %>%
        filter(reference_window == "partial window") %>%
        select(-reference_window),
      digits = 1,
      caption = paste("SUPPLEMENTAL - rank and sign changes by",
                      "season for the partial-window months."))
```

# Section 8 — Decision summary (recorded 2026-07-19)

The project owner reviewed the accepted full-history version of this
report and recorded the decision below (gate step 8 in
`docs/roadmap.md`; the policy is also recorded in
`docs/methodology.md`). The decision was made by the **project
owner** — this notebook performed no automatic selection.

- [ ] **Outcome A** — the record treated as sufficiently homogeneous
  with documented caveats *(not chosen)*.
- [x] **Outcome B — CHOSEN** — the Earth Engine Sentinel-5P OFFL
  record is usable for exploratory historical comparison **with
  explicit restrictions**; it must not be treated as an
  unconditionally homogeneous 2018–present trend record.
- [ ] **Outcome C** — official RPRO/Level-2 files outside Earth Engine
  required *(not chosen; remains a recorded future possibility in
  `docs/architecture.md` if rigorous trend analysis is ever needed)*.

**Owner decision (recorded 2026-07-19):**

- **Decision:** Outcome B, with the adopted baseline policy below.
- **Date:** 2026-07-19.
- **Rationale:** the accepted full-history audit and retrospective
  baseline-robustness study in this report (Sections 3–7): frequent
  contributor-scoped processor changes; signature-matched baselines
  unavailable for most targets (processor-matched: 93.6 % of target
  days, and completely unavailable for the evaluated 2026 targets);
  structurally partial early reference windows; and candidate coverage
  thresholds disproportionately removing winter observations.
- **Adopted baseline policy:**
  1. Use the previous three same-calendar years.
  2. Pool all valid daily BAAQMD regional means from those years.
  3. Baseline = median of that pooled historical sample.
  4. Signed anomaly = target daily regional mean − historical median.
  5. Percentile = percentage of historical values ≤ the target.
  6. Require all three requested prior years to supply at least one
     valid same-calendar-month observation before presenting the
     official anomaly or percentile.
  7. When the reference window is structurally partial, retain and
     display the raw daily satellite value and valid-area fraction,
     but report the baseline/anomaly/percentile as unavailable because
     the full historical window is not represented.
  8. Do not require exact processor-version or algorithm-version
     matching — the retrospective audit showed those variants are
     unavailable for most targets and completely unavailable for the
     evaluated 2026 targets.
  9. Do not calculate processor correction factors.
  10. Apply no hard valid-area-fraction exclusion to the baseline;
      retain every valid retrieval and expose the valid-area fraction
      — the audit showed candidate thresholds disproportionately
      remove winter observations.
  11. Continue retaining and flagging days with contributing
      non-NOMINAL products.
  12. Disclose processor/algorithm changes and state that the result
      is an exploratory rolling comparison — not a homogeneous
      long-term trend, causal processor analysis, surface
      concentration, AQI, health measure, or final episode
      classification.
- **Follow-up actions:** documentation updated the same day
  (`docs/methodology.md`, `docs/roadmap.md`, `docs/data-sources.md`,
  `earthengine/README.md`). Exploration script 06 predates policy
  points 6–7 (it presents baseline statistics from partially
  represented windows); it is intentionally unchanged, and any
  user-facing feature presenting official anomalies or percentiles
  must implement the full-window availability rule. No calculations in
  this notebook and no Earth Engine export script were modified as
  part of recording this decision. Episode thresholds, persistence
  rules, and spatial-extent rules remain undefined and are outside
  this decision.

# Unresolved limitations

- Satellite tropospheric columns and surface concentrations are
  different quantities; nothing here validates against surface
  monitors (gate step 7 remains future work).
- Regime differences are confounded with season, meteorology, emission
  trends (including the 2020 pandemic period), and coverage changes;
  no causal attribution to retrieval processing is possible from this
  audit alone.
- The EPSG:3310 / 7000 m statistics configuration is a fixed reference
  for this audit only — the final analysis scale is undecided.
- Daily `contributing_*` metadata columns are contributor-scoped by
  design; the collection-wide metadata record (every
  footprint-intersecting asset) lives in the product table, and the two
  timelines are kept separate throughout this notebook.
- The day-level contributor-regime convention (runs of contributor
  processor signatures) is a diagnostic construction, not a decided
  stratification.
- The export end is conservative: the latest represented local date is
  excluded because its ingestion may still be partial at export time
  (both dates are recorded in the manifest). Earlier recent dates may
  also still receive products under OFFL publication latency; re-run
  the current-year export to refresh.
- Retrospective robustness comparisons (Section 7) are conditional on
  availability: a variant is compared only on days where both it and
  the prior-three-years reference produce a value, so days lost to
  mixed or unavailable signatures are absent from the agreement
  metrics (their frequency is reported separately as unavailability).
- The full-window / partial-window distinction records structural
  representation only — whether every requested prior year supplied
  at least one valid day after the variant's signature or coverage
  filtering, where applicable. It is not a sample-size adequacy
  judgment, and the SUPPLEMENTAL partial-window summaries are
  structurally incomplete — not directly equivalent to the full
  three-year baseline.
- Signature matching in Section 7 uses exact raw contributor-scoped
  metadata strings with no version normalization (script 06's
  normalization is a display convention of that script). A change in
  raw formatting alone (e.g., the zero-padded "02.09.01") would
  register as a signature change; in this export each processor
  release appears under a single raw spelling.
- The prior-years-separate decomposition, the merged
  transition-period windows, and the coverage candidates of Section 7
  are audit display conventions and sensitivity candidates — none is
  decided methodology, and no baseline restriction or coverage
  threshold is selected by this notebook.
- No persistence rule, spatial-extent rule, or episode label is
  defined or implied here. The historical-baseline policy and the
  no-hard-coverage-exclusion rule recorded in Section 8 are project
  owner decisions (2026-07-19), informed by — but not computed by —
  this notebook.

# Session info

```{r session-info}
sessionInfo()
```
